From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-30 Pi+/paper/ufin.tex
removed bad diagram in ufin

\begin{center}
\begin{tikzpicture}[scale=1,every node/.style={scale=1}]
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}
\node[ultra thick, draw=blue, ellipse, minimum width=300pt, minimum height=300pt, align=center] {};
\node[ultra thick, draw=blue, ellipse, minimum width=70pt, minimum height=40pt, align=center] (a) {$\{ 1 , 2 \} \uplus \{ 3 \}$};
\node[ultra thick, draw=blue, ellipse, minimum width=70pt, minimum height=40pt, align=center] (b) at ([shift=({70pt,-70pt})]a) {$\{ 1 \} \uplus \{ 2, 3 \}$};
\node[ultra thick, draw=blue, ellipse, minimum width=70pt, minimum height=40pt, align=center] (c) at
([shift=({-70pt,-70pt})]a) {$\{ 10 \} \uplus \{ 20, 30 \}$};
\node (d) at ([shift=({50pt,-10pt})]a) {$\cdots$};
\draw[thick,-] (a) to node[draw=none,right] {$\equiv$} (b);
\draw[thick,-] (b) to node[draw=none,below] {$\equiv$} (c);
\draw[thick,-] (a) to node[draw=none,left] {$\equiv$} (c);
\end{tikzpicture}
\end{center}

>>>>

% \begin{center}
% \begin{tikzpicture}[scale=1,every node/.style={scale=1}]
% \usetikzlibrary{arrows}
% \usetikzlibrary{shapes}
% \node[ultra thick, draw=blue, ellipse, minimum width=300pt, minimum height=300pt, align=center] {};
% \node[ultra thick, draw=blue, ellipse, minimum width=70pt, minimum height=40pt, align=center] (a) {$\{ 1 , 2 \} \uplus \{ 3 \}$};
% \node[ultra thick, draw=blue, ellipse, minimum width=70pt, minimum height=40pt, align=center] (b) at ([shift=({70pt,-70pt})]a) {$\{ 1 \} \uplus \{ 2, 3 \}$};
% \node[ultra thick, draw=blue, ellipse, minimum width=70pt, minimum height=40pt, align=center] (c) at
% ([shift=({-70pt,-70pt})]a) {$\{ 10 \} \uplus \{ 20, 30 \}$};
% \node (d) at ([shift=({50pt,-10pt})]a) {$\cdots$};
% \draw[thick,-] (a) to node[draw=none,right] {$\equiv$} (b);
% \draw[thick,-] (b) to node[draw=none,below] {$\equiv$} (c);
% \draw[thick,-] (a) to node[draw=none,left] {$\equiv$} (c);
% \end{tikzpicture}
% \end{center}
